Improving phase-matching of FWM with temperature

### 2015-09-21 latex/article.tex
aggregation

We can also define a length scale, known as the coherence length, using $L_{coh} = 2\pi/|\Delta\kappa|$, where $\Delta\kappa$ is the maximum value of the effective phase mismatch that can be tolerated.
Moreover significant FWM occurs if $L_{sam}<L_{coh}$ where $L_{sam}$ is the sample length.
This definition allow us to make a further assumption, that is $\kappa = \Delta k + \gamma(P_1 + P_2) \approx \Delta k$.
Considering a pump power $P_1+P_2 = \SI{1}{\W}$ and a sample length $L_{sample} = \SI{1}{\cm}$ we obtain
\begin{equation}
\left\{
 	\begin{aligned}
		\gamma(P_1 + P_2) = \frac{n_2\omega}{cA_{eff}}P_0 = \frac{\SI{4.5e-18}{\m^2\per\W}}{}
		\Delta k &= 2\beta_P - \beta_S - \beta_I = 0
	\end{aligned}
\right.
\label{eq_f&pmc}
\end{equation}

since $\Delta k \gg \gamma(P_1 + P_2)$ almost always.
In order to be efficient, the parametric process needs to verify the conservation of both energy and momentum, as given in Eq. (\ref{eq_f&pmc}).

@@

\subsection{Data analysis}
We studied the value of $L_{coh}$ of the selected configurations with a rough analysis of 3D plots of $L_{coh}(\lambda,T_{H})$.
We observed the presence of different (mainly one or two) peaks in wavelength which were almost conserved in the temperature shift.

@@

\begin{figure}[h!]
	\centering
	\begin{subfigure}[b]{0.45\textwidth}
		\includegraphics[width=1\textwidth]{ppaat2.pdf}
		\label{fig_sym_pp@t2} 	% pp@t = bandwidth @ T_amb,
								% 2 = no points at 1.55um
		\caption{Peaks position at $T_{amb}$.}
	\end{subfigure}\hspace{.05\textwidth}
	\begin{subfigure}[b]{0.45\textwidth}
		\includegraphics[width=1\textwidth]{ppc2.pdf}
		\label{fig_sym_ppc2} % ppc = bandwidth change
		\caption{Change of peak position.}
	\end{subfigure}
	\caption{Peak position summary}
	\label{fig_sym_pp}
\end{figure}

\begin{figure}[h!]
	\centering
	\begin{subfigure}[b]{0.45\textwidth}
		\includegraphics[width=1\textwidth]{baat2.pdf}
		\label{fig_sym_b@t2} % b@t = bandwidth @ T_amb
		\caption{Bandwidth at $T_{amb}$.}
	\end{subfigure}\hspace{.05\textwidth}
	\begin{subfigure}[b]{0.45\textwidth}
		\includegraphics[width=1\textwidth]{bc2.pdf}
		\label{fig_sym_bc2} % bc = bandwidth change
		\caption{Change of bandwidth.}
	\end{subfigure}
	\caption{Bandwidth summary}
	\label{fig_sym_bw}
\end{figure}

>>>>

We can also define a length scale, known as the coherence length, using $L_{coh} = 2\pi/|\Delta\kappa|$, where $\Delta\kappa$ is the maximum value of the effective phase mismatch that can be tolerated.
Moreover significant FWM occurs if $L_{sam}<L_{coh}$ where $L_{sam}$ is the sample length.
This definition allow us to make a further assumption, that is $\kappa = \Delta k + \gamma(P_1 + P_2) \approx \Delta k$.
Considering a pump power $P_1+P_2 = \SI{1}{\W}$ and a sample length $L_{sample} = \SI{1}{\cm}$ we obtain
\begin{equation*}
\left\{
 	\begin{aligned}
		\gamma(P_1 + P_2) &= \frac{n_2\omega}{cA_{eff}}P_0 = \frac{\SI{4.5e-18}{\m^2\per\W}}{c\SI{e-12}{\m^2}}\frac{2\pi c}{\SI{1.55e-6}{\m}}\SI{1}{\W} \approx \SI{20}{\per\m} \approx \SI{e1}{\per\m}\\
		|\Delta k |&= \frac{2\pi}{L_{sam}} = \frac{2\pi}{\SI{1}{\cm}} \approx \SI{600}{\per\m} \approx \num{e2} - \SI{e3}{\per\m}
	\end{aligned}
\right.
\label{eq_f&pmc}
\end{equation*}

since |$\Delta k| \gg \gamma(P_1 + P_2)$ almost always we can consider it trascurable.

Therefore, in order to be efficient, the parametric process needs to verify the conservation of both energy and momentum, as given in Eq. (\ref{eq_f&pmc}).

@@

\subsection{Data analysis}

We studied the value of $L_{coh}$ of the selected configurations with a rough analysis of 3D plots of $L_{coh}(\lambda,T_{H})$.
We observed the presence of different (mainly one or two) peaks in wavelength which were almost conserved in the temperature shift.

@@

\begin{figure}[h!]
	\centering
	\begin{subfigure}[b]{0.75\textwidth}
		\includegraphics[width=1\textwidth]{ppaat2.png}
		\label{fig_sym_pp@t2} 	% pp@t = bandwidth @ T_amb,
								% 2 = no points at 1.55um
		\caption{Peaks position at $T_{amb}$.}
	\end{subfigure}
	\begin{subfigure}[b]{0.75\textwidth}
		\includegraphics[width=1\textwidth]{ppc2.png}
		\label{fig_sym_ppc2} % ppc = bandwidth change
		\caption{Change of peak position.}
	\end{subfigure}
	\caption{Peak position summary}
	\label{fig_sym_pp}
\end{figure}

\begin{figure}[h!]
	\centering
	\begin{subfigure}[b]{0.75\textwidth}
		\includegraphics[width=1\textwidth]{baat2.png}
		\label{fig_sym_b@t2} % b@t = bandwidth @ T_amb
		\caption{Bandwidth at $T_{amb}$.}
	\end{subfigure}
	\begin{subfigure}[b]{0.75\textwidth}
		\includegraphics[width=1\textwidth]{bc2.png}
		\label{fig_sym_bc2} % bc = bandwidth change
		\caption{Change of bandwidth.}
	\end{subfigure}
	\caption{Bandwidth summary}
	\label{fig_sym_bw}
\end{figure}
